---
title: "Data Import"
output: github_document
---

```{r setup, echo = FALSE, message = FALSE}
library(tidyverse)
library(janitor)
library(readxl)
library(haven)
```




## Import the FAS Litters CSV

```{r}
litters_df = read.csv("data/FAS_litters.csv")

litters_df = janitor::clean_names(litters_df) #这里可以不用load janitor packages, 这样就不用把整个packages都加载出来，只调用其中一个即可。并且好多packages里面有相同名字的function
```

## Look at the dataset
```{r}
litters_df

head(litters_df)
tail(litters_df)
```

```{r eval = FALSE} 
# eval = FALSE create a new window to present the dataset. Always using this command when viewing dataset
view(litters_df)
```

Use relative paths.

```{r}
pups_df = read.csv("data/FAS_pups.csv")

pups_df = janitor::clean_names(pups_df)

pups_df
```

Use absolute paths.

```{r eval = FALSE}
pups_df = read_csv("/Users/yiran/Library/Mobile Documents/com~apple~CloudDocs/Desktop/徐逸然yyds/学习/MS/Coursework/2023-2024 Fall/BISTP8105_Data Science I/Lecture 4/data_wrangling_i/data/FAS_pups.csv")

```

## Loom at read_csv options
Skip the header according to the formatting using 'skip = '

```{r}
litters_df = 
  read_csv(
    file = "data/FAS_litters.csv",
    skip = 2
  )

```

What about missing data
发现 GDDWeight这一列的type显示的是chr，但实际上它是数字，是因为他有一个entry是'.',所有整列都归位chr

```{r}
litters_df = 
  read_csv(
    file = "data/FAS_litters.csv",
    na = c("NA", "", ".")
  )

litters_df = janitor::clean_names((litters_df))

```

What if we code 'group' as a factor variable

```{r}
litters_df = 
  read_csv(
    file = "data/FAS_litters.csv",
    na = c("NA", "", "."),
    col_types = cols(
      Group = col_factor()
    )
  )
```


## Import and excel file

Import MLB 2011 summary data.

```{r}
mlb_df = read_excel("data/mlb11.xlsx", sheet = "mlb11")
```

```{r}
pulse_df = read_sas("data/public_pulse_data.sas7bdat")

pulse_df
```

## Never use read.csv(), use read_csv(): 后者输出一个tibble，而不是dataframe，会包含更多信息，会更robust

```{r}
litters_df = read.csv("data/FAS_litters.csv")
```

Never do this either: don't use "$"

```{r}
litters_df$L
```

